Improved Association in a Classical Density-Functional Theory for Water

### 2013-09-04 papers/water-saft/paper.tex
Added abstract, changed title for water paper. Tested on node32. Took 0:21.72.

\begin{document}
\title{A Classical Density-Functional Theory for Describing Water Interfaces}

@@

\begin{abstract}
We develop an improved version of our old functional.
\end{abstract}
\maketitle

>>>>

\begin{document}
\title{Improved Association in a Classical Density-Functional Theory
  for Water}

@@

\begin{abstract}
We present a modification to the classical density-functional theory
(DFT) for water by Hughes \emph{et al.} which uses Statistical
Associating Fluid Theory(SAFT-VR) for attractive interactions. We
modify the association contribution to the free energy to use an
improved radial distribution function $g_\sigma^{HS}$. We study the
difference between the two functionals density profile, number
of broken hydrogen bonds for hard rods in water, and the number of
broked hydrogen bonds for a hard sphere in water.
\end{abstract}
\maketitle
